Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-06 paper/ms.tex
I don't have energy to finish this non-critical par. today
switch to aastex6.1

\documentclass[manuscript]{aastex6}

@@

\include{aastexmods}

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\usepackage[flushleft]{threeparttable}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}
\bibliographystyle{aasjournal.bst}

@@

\author{
  Semyeong Oh\altaffilmark{\pu,\lead},
  Adrian M. Price-Whelan\altaffilmark{\pu},
  John M. Brewer\altaffilmark{\yale},
  Keith A. Hawkins\altaffilmark{\columbia},
  Nathan W. C. Leigh\altaffilmark{\amnh},
  David W. Hogg\altaffilmark{\ccpp,\mpia,\cca},
  David N. Spergel\altaffilmark{\pu,\cca},
  Justin Myles\altaffilmark{\yale} \etal\
}

% Affiliations
\newcommand{\pu}{1}
\newcommand{\lead}{2}
\newcommand{\yale}{3}
\newcommand{\columbia}{4}
\newcommand{\amnh}{5}
\newcommand{\ccpp}{6}
\newcommand{\mpia}{7}
\newcommand{\cca}{8}

\altaffiltext{\pu}{Department of Astrophysical Sciences,
  Princeton University, 4 Ivy Ln, Princeton, NJ 08544, USA}
\altaffiltext{\lead}{To whom correspondence should be addressed:
  \texttt{semyeong@astro.princeton.edu}}
\altaffiltext{\columbia}{Department of Astronomy,
  Columbia University, 550 W 120th St, New York, NY 10027, USA}
\altaffiltext{\yale}{Department of Astronomy,
  Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
\altaffiltext{\amnh}{Department of Astrophysics,
  American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics,
  Department of Physics,
  New York University, 4 Washington Place,
  New York, NY 10003, USA}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie,
  K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cca}{Center for Computational Astrophysics,
  Flatiron Institute, 162 5th Ave, New York, NY 10003, USA}

@@

{\bf HD~20782/HD~20782:} 
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
4.2~arcmin sky separation). Both stars in this system host close-in giant
planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
Neptune-mass planets within 0.3~AU with moderately high eccentricity
($e\sim0.1-0.3$) \footnote{
  The two stars were monitored by \project{HARPS}
  campaign, and it has recently been reported by \citealt{} that HD~20781 hosts
  four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le
  0.11$ within $\approx 0.35$~AU.}.
They found that the abundances of 15 elements between the two stars are
consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of
$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
planet migration.

@@

Finally, \citealt{Biazzo:2015aa}

>>>>

\documentclass[modern, letterpaper]{aastex61}
% \documentclass[twocolumn]{aastex61}

@@

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\usepackage[flushleft]{threeparttable}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}
\bibliographystyle{aasjournal}

@@

\author{Semyeong Oh} % TODO: need ORCID
\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}
\affil{To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}}

\author{John M. Brewer} % TODO: need ORCID
\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}

\author[0000-0003-0872-7098]{Adrian M. Price-Whelan}
\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}

\author[0000-0003-2866-9403]{David W. Hogg}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, room 1005, New York, NY 10003, USA}
\affil{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
\affil{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg}

\author{David N. Spergel} % TODO: need ORCID
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}

% \author{Keith A. Hawkins}
% \affil{Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA}

% \author{Nathan W. C. Leigh}
% \affil{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}

\author{Justin Myles} % TODO: need ORCID
\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}

@@

{\bf HD~20782/HD~20782:}
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
4.2~arcmin sky separation). Both stars in this system host close-in giant
planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
Neptune-mass planets within 0.3~AU with moderately high eccentricity
($e\sim0.1-0.3$) \footnote{
  The two stars were monitored by \project{HARPS}
  campaign, and it has recently been reported by \citealt{todo} that HD~20781 hosts
  four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le
  0.11$ within $\approx 0.35~{\rm AU}$.}.
They found that the abundances of 15 elements between the two stars are
consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of
$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
planet migration.

@@

%TODO: summarize Biazzo+ on XO-2
%Finally, \citealt{Biazzo:2015aa}
